DATA DRIVEN MODELS FOR APOGEE M DWARFS

### 2018-07-03 paper/draft1/draft1.tex
add mann result table

\usepackage{color}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathrsfs}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/west_self_test_spt.png}
\end{center}
\caption{Spectral type model: training label vs. test label.} \label{fig:west_selftest}
\end{figure}

\subsection{Temperature/Metallicity Model}
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/self_and_validation_test_teff.png}
\includegraphics[width=16cm]{figures/self_and_validation_test_fe_h.png}
\end{center}
\caption{Temperature and Metallicity label self test.} \label{fig:mann_selftest}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=12cm]{figures/west_spt_derivative.png}
\end{center}
\caption{Derivative plots for spectral type model.} \label{fig:west_derivative}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=15cm]{figures/derivative_jackknife_teff.png}
\includegraphics[width=15cm]{figures/derivative_jackknife_feh.png}
\end{center}
\caption{Derivative plots for physical parameter model. \textit{Top:} Derivative of flux with repsect to temperature. \textit{Bottom:} Derivative of flux with repsect to metallicity.} \label{fig:mann_derivative}
\end{figure}

>>>>

\usepackage{color}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{booktabs}

@@

\newpage

\begin{figure}[ht]
\begin{center}
\includegraphics[width=18cm]{figures/self_and_validation_test_spt.png}
\end{center}
\caption{Spectral type model: training label vs. test label.} \label{fig:west_selftest}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=18cm]{figures/self_and_validation_test_teff.png}
\includegraphics[width=18cm]{figures/self_and_validation_test_fe_h.png}
\end{center}
\caption{Temperature and Metallicity label self test.} \label{fig:mann_selftest}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/derivative_jackknife_spt.png}
\end{center}
\caption{Derivative plots for spectral type model taken at the median training spectral type, SPT$=3$.} \label{fig:west_derivative}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/derivative_jackknife_teff.png}
\includegraphics[width=16cm]{figures/derivative_jackknife_feh.png}
\end{center}
\caption{Derivative plots for physical parameter model. \textit{Top:} Derivative of flux with repsect to temperature taken at the median training temperature, T$_{\rm eff}=3463K$. \textit{Bottom:} Derivative of flux with repsect to metallicity taken at the median training metallicity, [Fe/H]$=-0.03$ dex.} \label{fig:mann_derivative}
\end{figure}

%%==========================================================================================
%% Tables

\newpage

% \begin{longrotatetable}
\startlongtable
\begin{deluxetable*}{ccc|ccc|ccc}
\tablecaption{Cannon results for Temperature/Metallicity model \label{mann_results}}
\tabletypesize{\scriptsize}
\tablehead{
% \colhead{Designation} & \colhead{RA} & \colhead{DEC} & \colhead{$T_{\rm eff}$} & \colhead{[Fe/H]} \\
% \colhead{(2MASS)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{(K)} & \colhead{(dex)}
\multicolumn{3}{c}{\underline{Designation}} & \multicolumn{3}{c}{\underline{Temperature (K)}} & \multicolumn{3}{c}{\underline{Metallicity (dex)}} \\
	  \colhead{2MASS ID} & \colhead{RA}   & \colhead{DEC}
    & \colhead{Training} & \colhead{Test} & \colhead{LOOCV}
    & \colhead{Training} & \colhead{Test} & \colhead{LOOCV}  
} 
\startdata
2M00182256+4401222 & 4.59542   & 44.02278  & 3603        & 3532       & 3519        & -0.3       & -0.27     & -0.24      \\
2M00182549+4401376 & 4.60779   & 44.02734  & 3218        & 3527       & 3554        & -0.3       & -0.28     & -0.27      \\
2M00285391+5022330 & 7.22488   & 50.37588  & 3207        & 3185       & 3188        & 0.11       & 0.05      & 0.02       \\
2M00401001+0308050 & 10.04169  & 3.13473   & 3725        & 3783       & 3778        & 0.04       & 0.11      & 0.13       \\
2M00580115+3919111 & 14.50482  & 39.31977  & 3157        & 3094       & 3101        & -0.07      & -0.01     & 0.03       \\
2M01232542+1638384 & 20.8559   & 16.64401  & 3272        & 3218       & 3217        & 0.1        & 0.03      & 0.0        \\
2M02001278+1303112 & 30.05402  & 13.05196  & 3080        & 3057       & 3074        & -0.16      & -0.1      & -0.01      \\
2M02361535+0652191 & 39.06358  & 6.87167   & 3284        & 3249       & 3253        & -0.12      & -0.29     & -0.29      \\
2M03044335+6144097 & 46.18104  & 61.73583  & 3500        & 3468       & 3467        & -0.12      & -0.26     & -0.27      \\
2M03553688+5214291 & 58.90373  & 52.2414   & 3435        & 3381       & 3369        & -0.35      & -0.25     & -0.18      \\
2M04125880+5236421 & 63.24499  & 52.61165  & 3100        & 3181       & 3200        & -0.04      & -0.01     & 0.01       \\
2M04310001+3647548 & 67.75003  & 36.79855  & 3419        & 3371       & 3369        & 0.08       & 0.11      & 0.1        \\
2M05030563+2122362 & 75.77354  & 21.37664  & 3155        & 3290       & 3503        & 0.06       & -0.15     & -0.36      \\
2M05222053+3031097 & 80.58561  & 30.51933  & 3389        & 3417       & 3426        & 0.28       & 0.2       & 0.14       \\
2M05312734-0340356 & 82.86417  & -3.67722  & 3801        & 3820       & 3854        & 0.49       & 0.49      & 0.37       \\
2M05413073+5329239 & 85.37804  & 53.48987  & 3765        & 3752       & 3755        & 0.19       & 0.15      & 0.13       \\
2M05420897+1229252 & 85.53833  & 12.48956  & 3250        & 3226       & 3235        & -0.22      & -0.34     & -0.31      \\
2M06000351+0242236 & 90.01458  & 2.70657   & 3214        & 3164       & 3165        & 0.07       & 0.05      & 0.03       \\
2M06011106+5935508 & 90.2961   & 59.59713  & 3340        & 3258       & 3255        & -0.09      & -0.05     & -0.03      \\
2M06112610+1032599 & 92.8588   & 10.54998  & 3636        & 3711       & 3698        & -0.39      & -0.42     & -0.39      \\
2M06544902+3316058 & 103.70411 & 33.26823  & 3448        & 3364       & 3359        & -0.02      & 0.04      & 0.06       \\
2M07171706-0501031 & 109.32108 & -5.01754  & 3193        & 3159       & 3168        & -0.09      & -0.12     & -0.09      \\
2M07272450+0513329 & 111.852   & 5.2263    & 3317        & 3285       & 3285        & -0.11      & -0.2      & -0.19      \\
2M07444018+0333089 & 116.16744 & 3.55252   & 3217        & 3176       & 3174        & 0.23       & 0.26      & 0.15       \\
2M08031949+5250387 & 120.83131 & 52.84402  & 3508        & 3622       & 3626        & -0.26      & -0.24     & -0.24      \\
2M08083284+5304377 & 122.13679 & 53.07712  & 3398        & 3280       & 3273        & 0.0        & 0.08      & 0.09       \\
2M08103429-1348514 & 122.64277 & -13.81427 & 3544        & 3517       & 3515        & 0.0        & 0.0       & 0.0        \\
2M08155393+3136392 & 123.97459 & 31.61077  & 3753        & 3810       & 3821        & 0.16       & 0.07      & 0.03       \\
2M08323599+4510175 & 128.14998 & 45.17153  & 3494        & 3505       & 3506        & -0.14      & -0.21     & -0.21      \\
2M08370799+1507475 & 129.28319 & 15.12944  & 3596        & 3553       & 3552        & -0.17      & -0.26     & -0.27      \\
2M08524084+2818589 & 133.17018 & 28.31634  & 3166        & 3213       & 3239        & 0.31       & 0.5       & 0.27       \\
2M08585633+0828259 & 134.73479 & 8.47384   & 3200        & 3142       & 3147        & -0.04      & -0.09     & -0.08      \\
2M09142298+5241125 & 138.595   & 52.68639  & 3920        & 3900       & 3879        & -0.01      & -0.02     & 0.01       \\
2M09174473+4612246 & 139.4363  & 46.20685  & 3478        & 3548       & 3556        & 0.04       & -0.02     & -0.03      \\
2M09214911+4330284 & 140.45447 & 43.50784  & 3170        & 3196       & 3206        & 0.16       & 0.23      & 0.19       \\
2M09285333-0722148 & 142.22221 & -7.37095  & 3508        & 3445       & 3440        & -0.27      & -0.23     & -0.22      \\
2M10112218+4927153 & 152.84254 & 49.45431  & 4131        & 4007       & 3946        & 0.24       & 0.22      & 0.23       \\
2M10121768-0344441 & 153.07364 & -3.74563  & 3623        & 3619       & 3620        & 0.13       & 0.16      & 0.16       \\
2M10193634+1952122 & 154.90117 & 19.87002  & 3370        & 3384       & 3389        & 0.15       & 0.24      & 0.21       \\
2M10285555+0050275 & 157.23155 & 0.8411    & 3548        & 3517       & 3515        & -0.18      & -0.16     & -0.15      \\
2M10331367+3409120 & 158.30687 & 34.15333  & 3500        & 3518       & 3518        & -0.15      & -0.19     & -0.2       \\
2M10350859+3349499 & 158.7858  & 33.83055  & 3816        & 3906       & 3907        & -0.04      & 0.01      & 0.03       \\
2M10453795+1833111 & 161.4081  & 18.55306  & 3673        & 3773       & 3780        & 0.14       & 0.13      & 0.13       \\
2M10505201+0648292 & 162.71704 & 6.80826   & 3238        & 3258       & 3265        & 0.16       & 0.18      & 0.12       \\
2M10520440+1359509 & 163.01762 & 13.99756  & 3298        & 3230       & 3228        & -0.13      & -0.11     & -0.07      \\
2M11000432+2249592 & 165.01781 & 22.833    & 3463        & 3426       & 3423        & -0.11      & -0.1      & -0.09      \\
2M11032023+3558117 & 165.83423 & 35.97054  & 3563        & 3682       & 3551        & -0.38      & -0.58     & -0.39      \\
2M11052903+4331357 & 166.36992 & 43.52665  & 3619        & 3547       & 3525        & -0.37      & -0.34     & -0.3       \\
2M11054316+1014093 & 166.42966 & 10.23605  & 3439        & 3395       & 3393        & -0.03      & -0.06     & -0.07      \\
2M11091225-0436249 & 167.30106 & -4.60695  & 3661        & 3743       & 3748        & -0.03      & -0.09     & -0.1       \\
2M11263270+2145262 & 171.63622 & 21.75719  & 3610        & 3642       & 3642        & -0.18      & -0.16     & -0.15      \\
2M11273856+0358359 & 171.91071 & 3.97664   & 3920        & 3932       & 3963        & 0.43       & 0.44      & 0.31       \\
2M11474074+0015201 & 176.9198  & 0.25553   & 3261        & 3235       & 3236        & 0.1        & 0.23      & 0.22       \\
2M11474440+0048164 & 176.93491 & 0.80473   & 3192        & 3155       & 3157        & -0.02      & -0.06     & -0.06      \\
2M11530522+1855480 & 178.27184 & 18.93002  & 3773        & 3760       & 3752        & -0.14      & -0.08     & -0.06      \\
2M12192028+1323524 & 184.83449 & 13.39793  & 3926        & 3954       & 3945        & 0.0        & 0.13      & 0.18       \\
2M12274471-0315006 & 186.93625 & -3.25018  & 3355        & 3399       & 3407        & 0.19       & 0.2       & 0.17       \\
2M12390461+4702234 & 189.76958 & 47.03974  & 3492        & 3447       & 3445        & 0.05       & 0.06      & 0.06       \\
2M12470102+4637334 & 191.75412 & 46.62587  & 3571        & 3543       & 3544        & 0.22       & 0.23      & 0.22       \\
2M13113464+1306461 & 197.89433 & 13.11282  & 3459        & 3407       & 3402        & -0.1       & -0.03     & -0.01      \\
2M13160127+1415504 & 199.00528 & 14.26403  & 3686        & 3768       & 3775        & -0.06      & -0.16     & -0.17      \\
2M13295979+1022376 & 202.49895 & 10.37731  & 3727        & 3674       & 3669        & -0.09      & -0.13     & -0.13      \\
2M13345147+3746195 & 203.71442 & 37.7721   & 3273        & 3247       & 3250        & 0.14       & 0.13      & 0.08       \\
2M13400879+4346380 & 205.03676 & 43.77729  & 3332        & 3322       & 3325        & -0.19      & -0.18     & -0.14      \\
2M13454354+1453317 & 206.43251 & 14.89139  & 3649        & 3688       & 3677        & -0.31      & -0.37     & -0.36      \\
2M15290936+5724418 & 232.28886 & 57.41167  & 3660        & 3719       & 3723        & -0.09      & -0.14     & -0.14      \\
2M15594729+4403595 & 239.94707 & 44.06654  & 3526        & 3614       & 3632        & 0.05       & 0.02      & 0.01       \\
2M16252459+5418148 & 246.35249 & 54.30413  & 3475        & 3407       & 3400        & -0.35      & -0.25     & -0.22      \\
2M16541202+1154529 & 253.5502  & 11.91464  & 3834        & 3760       & 3697        & -0.48      & -0.38     & -0.29      \\
2M17093153+4340531 & 257.38138 & 43.68139  & 3284        & 3242       & 3242        & 0.2        & 0.25      & 0.17       \\
2M17362594+6820220 & 264.10803 & 68.33932  & 3439        & 3487       & 3492        & 0.05       & -0.21     & -0.23      \\
2M18161819+0131277 & 274.07575 & 1.5243    & 3391        & 3350       & 3347        & -0.25      & -0.19     & -0.17      \\
2M18244689-0620311 & 276.1954  & -6.342    & 3412        & 3386       & 3384        & 0.01       & 0.07      & 0.08       \\
2M18424666+5937499 & 280.69489 & 59.63015  & 3441        & 3386       & 3385        & -0.23      & -0.32     & -0.32      \\
2M18424688+5937374 & 280.6958  & 59.62659  & 3345        & 3391       & 3400        & -0.3       & -0.35     & -0.33      \\
2M18451027+0620158 & 281.29282 & 6.33774   & 3674        & 3684       & 3688        & 0.02       & 0.03      & 0.03       \\
2M19142541+1755081 & 288.6059  & 17.91894  & 3725        & 3830       & 3835        & -0.08      & -0.09     & -0.09      \\
2M19165526+0510086 & 289.23032 & 5.16909   & 3558        & 3536       & 3538        & 0.1        & 0.08      & 0.07       \\
2M19500252+3235012 & 297.51022 & 32.58347  & 3385        & 3214       & 3215        & -0.18      & -0.31     & -0.28      \\
2M19535443+4424541 & 298.47977 & 44.41508  & 2859        & 2801       & 2889        & -0.05      & 0.08      & 0.19       \\
2M20032651+2952000 & 300.86075 & 29.86652  & 3144        & 3164       & 3178        & 0.06       & -0.03     & -0.09      \\
2M20531977+6209156 & 313.33246 & 62.1545   & 3791        & 3728       & 3712        & -0.06      & 0.04      & 0.08       \\
2M21065473+3844265 & 316.73013 & 38.74202  & 4021        & 4004       & 3922        & -0.22      & -0.23     & -0.11      \\
2M22464980+4420030 & 341.70737 & 44.33405  & 3298        & 3236       & 3235        & 0.03       & 0.03      & 0.02       \\
2M22563497+1633130 & 344.14517 & 16.55347  & 3720        & 3689       & 3688        & 0.21       & 0.29      & 0.28       \\
2M23060482+6355339 & 346.52011 & 63.92622  & 3700        & 3770       & 3780        & 0.19       & 0.14      & 0.11       \\
2M23315208+1956142 & 352.96732 & 19.93727  & 3353        & 3278       & 3274        & 0.03       & 0.05      & 0.05       \\
2M23315244+1956138 & 352.9689  & 19.93719  & 3072        & 3266       & 3296        & 0.03       & 0.04      & 0.03       \\
2M23491255+0224037 & 357.30206 & 2.40136   & 3646        & 3604       & 3560        & -0.45      & -0.46     & -0.4    
\enddata
\end{deluxetable*}
% \end{longrotatetable}
